What do incoming university students believe about open science practices in

### 2021-02-09 analysis/Manuscript.Rmd
starting to import data

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

@@

@@

@@

>>>>

```{r setup, include = FALSE}
library(papaja)
library(here)
library(tidyverse)

r_refs("r-references.bib")
```

@@

```{r import data}

#import the data. 
df2 <- read.csv (here::here("data", "students_processed.csv"))
# [[breadcrumbs: work on parsing the columns. It could be that I didn't need to 
# write them as factors in the preprocessing]]
df3 <- read.csv (here::here("data", "students_processed.csv"), 
                 colClasses = c('numeric','factor','factor',
                                rep('character', 3),
                                rep('factor', 2), 'character', 
                                rep('numeric', 35), rep('character', 3),
                                rep('factor', 4), rep('character', 2),
                                rep('factor', 21))
                 )

# # import the metadata [check if I need it for these analyses?]
# metadata <- here::here("survey", "data", "os_metadata_raw_data.csv") %>% 
#   read_csv(col_names = TRUE, skip_empty_rows = TRUE) %>% 
#   filter(!is.na(OldVariable))
```

@@

```{r eligibility}

# I fell down a massive git hub hole, so I'll make progress on this tomorrow!

```

@@

```{r demographics}

```
